% Sarbagya Gho Shrestha - Professional Resume
\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}

% Formatting
\titleformat{\section}{\large\bfseries\uppercase}{}{0em}{}[\titlerule]
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\hypersetup{colorlinks=true, urlcolor=blue}

\begin{document}

% Header
{\centering
{\LARGE\textbf{Sarbagya Gho Shrestha}}\\[8pt]
\href{mailto:sarbagyaghoshrestha@gmail.com}{sarbagyaghoshrestha@gmail.com} $|$
+977 9851402011 $|$
Sanothimi, Bhaktapur\\
\href{https://linkedin.com/in/sarbagyashrestha}{linkedin.com/in/sarbagyashrestha} $|$
\href{https://github.com/sarbagya42}{github.com/sarbagya42} $|$
\href{https://sarbagyaghoshrestha.com.np}{sarbagyaghoshrestha.com.np}\\[10pt]
}

% Professional Summary
\textit{Tech Lead \& Full Stack Engineer driving Nepal's digital transformation through innovative governance solutions. Builder and innovator with expertise in scalable systems, civic tech, and emerging technologies. Passionate about bridging hardware and software, with creative pursuits in music.}\\

\section*{Work Experience}

\textbf{Ninja Infosys} \hfill \textbf{Jun. 2025 -- Present}\\
\textit{Project Manager \& Tech Lead} \hfill Kathmandu District, Nepal\\[-6pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item Leading technical architecture and project execution for Digital e-Palika platform serving \textbf{50+ municipalities} across Nepal, streamlining citizen services, revenue collection, and grievance handling.
    \item Architected and engineered \textbf{Integrated Content Management System (ICMS)} now powering \textbf{100+ government websites} nationwide with microservices architecture using Kafka and Kubernetes.
    \item Coordinate cross-functional teams, manage timelines, and align stakeholders to ensure successful delivery of features meeting real-world governance needs while maintaining system scalability and security.
    \item \textbf{Tech Stack:} Next.js, NestJS, Kafka, Kubernetes, PostgreSQL, Docker, Redis, CI/CD
\end{itemize}

\textbf{Intensive Study and Research Center} \hfill \textbf{Jan. 2025 -- Jun. 2025}\\
\textit{Full Stack Engineer \& DevOps Lead} \hfill Kathmandu, Nepal\\[-6pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item Architected and deployed \textbf{digital profile systems for 10+ municipalities} including Pokhara Metropolitan City in just \textbf{4 months with 2-person team} (with Trilochan Bhusal), serving 100,000+ citizens.
    \item Engineered comprehensive \textbf{Survey Management System (SMS)} with custom ODK Fetcher, processing \textbf{100,000+ survey responses} with real-time analytics dashboards and live monitoring capabilities.
    \item Directed end-to-end DevOps pipelines (CI/CD, Docker, AWS EC2/S3, Jenkins) ensuring resilient systems for resource-constrained regions with 99.9\% uptime.
    \item Led field training initiatives, empowering \textbf{300+ local officials and enumerators} with digital skills for sustainable civic digitization.
    \item \textbf{Tech Stack:} Next.js, NestJS, tRPC, PostgreSQL, MongoDB, Docker, AWS, ODK Collect/Central, Nginx, PM2
\end{itemize}

\textbf{Mandala Foods} \hfill \textbf{Present}\\
\textit{Tech Lead \& Optimization Engineer} \hfill Kathmandu, Nepal\\[-6pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item Leading technology and optimization initiatives for booming food systems startup founded by Dr. Robin Shrestha (Tufts University, USAID veteran) and innovative team focused on nutrition and circular economy.
    \item Architecting scalable technical solutions to support sustainable food systems and reduce agricultural loss and waste.
\end{itemize}

\textbf{Ibtidaa Softwares Pvt. Ltd.} \hfill \textbf{Oct. 2023 -- Dec. 2024}\\
\textit{Full Stack Developer \& Tech Lead} \hfill Nepal (Hybrid)\\[-6pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item Developed and maintained "Bidesh" App/Website using Next.js for RP Srijan Way To Success.
    \item Built Event Management and Visualization Tool using Django and JavaScript for Shramik Sanjal with Chart.js integration.
    \item \textbf{Tech Stack:} Next.js, NestJS, PostgreSQL, MongoDB, Express.js, Django REST Framework, Redux.js, Jenkins
\end{itemize}

\textbf{IEEE Pulchowk Student Branch} \hfill \textbf{Apr. 2023 -- Jun. 2024}\\
\textit{Chair \& Creative Director} \hfill Lalitpur District, Nepal\\[-6pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item Led IEEE Pulchowk Student Branch as Chair, organizing technical events, workshops, and coordinating student activities.
    \item Served as Creative Director managing visual communications and promotional content for the branch.
\end{itemize}

\textbf{PointZeroo} \hfill \textbf{Mar. 2022 -- Sep. 2022}\\
\textit{Frontend Developer} \hfill Nepal (Hybrid)\\[-6pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item Maintained e-commerce website and developed web application for SSoChe, Pulchowk Campus.
    \item \textbf{Tech Stack:} JavaScript, HTML5, CSS, React, MongoDB, Node.js
\end{itemize}

\section*{Key Projects}

\textbf{8-bit Breadboard Computer (Ben Eater Inspired)} \hfill \textbf{Jan. 2024 -- May 2024}\\
\textit{6th Semester Minor Project, IOE Pulchowk Campus}\\[-6pt]
\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item Built complete 8-bit computer from scratch using discrete logic ICs with team (Rohit Joshi, Yugal Pariyar).
    \item Innovatively created \textbf{custom 128-bit RAM module} due to IC unavailability, demonstrating problem-solving and determination.
    \item Implemented full architecture: ALU, control unit, registers, program counter, instruction decoder, clock module.
    \item Hardware-only project showcasing deep understanding of computer architecture from first principles.
\end{itemize}

\textbf{Digital Profile Platforms} -- Live: \href{https://pokhara.digprofile.com/en}{pokhara.digprofile.com}\\
\textbf{Survey Management System} -- Live: \href{https://duduwa-admin.vercel.app}{duduwa-admin.vercel.app}\\
\textbf{ICMS Platform} -- Demo: \href{http://sddodang.lumbini.gov.np/ne}{sddodang.lumbini.gov.np}

\section*{Education}

\textbf{Tribhuvan University, IOE, Pulchowk Campus} \hfill \textbf{May 2021 -- May 2025}\\
\textit{Bachelor of Engineering (B.E.) -- Electronics, Communication and Information Engineering} \hfill Lalitpur, Nepal\\
\textit{Achievements:} IEEE Chair, Creative Director, Pulchowk Music Club Executive Member

\textbf{SOS Hermann Gmeiner School} \hfill \textbf{2019 -- 2021}\\
\textit{+2 Science (Physics and Mathematics) -- Grade: A+} \hfill Sanothimi, Bhaktapur\\
\textit{Achievements:} Bestmanship Awardee 2019, Music Club President

\section*{Technical Skills}

\textbf{Languages:} TypeScript/JavaScript, Python, C/C++, Golang, SQL, Shell Scripting\\
\textbf{Frontend:} Next.js, React.js, Redux.js, HTML5, CSS/Tailwind CSS, Responsive Design\\
\textbf{Backend:} NestJS, Express.js, tRPC, Django, Django REST Framework, Node.js, Microservices\\
\textbf{Databases:} PostgreSQL, MongoDB, Redis, SQL, Data Modeling\\
\textbf{DevOps \& Cloud:} Docker, Kubernetes, Kafka, Jenkins, AWS (EC2, S3, Lambda), CI/CD, Nginx, PM2, Coolify\\
\textbf{Data Systems:} ODK Collect, ODK Central, Data Visualization, Real-time Analytics\\
\textbf{Hardware \& AI:} Embedded Systems, Digital Logic, Computer Architecture, Machine Learning, UAVs, Avionics

\section*{Areas of Interest}

\textbf{Digital Governance:} E-government solutions, civic tech, full-stack development for public administration\\
\textbf{AI \& Embedded Systems:} Machine learning, hardware design, UAVs, avionics, IoT applications\\
\textbf{Distributed Systems:} Scalable architectures, microservices, Kafka, Kubernetes, system design\\
\textbf{Creative Arts:} Music production and performance, 100K+ views on Instagram as music artist

\section*{Impact \& Achievements}

\begin{itemize}[leftmargin=*, itemsep=2pt, topsep=4pt]
    \item \textbf{100+ government websites} powered by ICMS platform at national scale
    \item \textbf{50+ municipalities} digitized through Digital e-Palika platform
    \item \textbf{10+ municipal digital profiles} deployed in 4 months with 2-person team
    \item \textbf{100,000+ citizen records} processed and \textbf{300+ officials} trained
    \item \textbf{Custom 128-bit RAM} built for 8-bit breadboard computer project
    \item \textbf{100K+ views} as music artist on Instagram, blending technology with creative arts
\end{itemize}

\vfill
\begin{center}
\textit{Empowering Nepal's digital transformation through innovative governance solutions.\\
Architecting the future of public administration with precision and purpose.}
\end{center}

\end{document}
